The Resurgence of the linear optics interferometer --- recent advances \& applications

### 2017-05-09 paper.tex
Edited intro

\comment{To do}

Technical advancements have been made on many fronts. It is possible now to put single-photon sources and linear-optical networks on a silica chip. The advantage of using such integrated photonics over bulk optics is that it is more stable against phase fluctuations, and miniaturized. This increases the scalability of optical implementations of quantum information protocols.

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=0.7\columnwidth]{reck}
\caption{Efficient decomposition of arbitrary linear optics networks into a sequence of beamsplitters and phase-shifters.} \label{fig:Reck}	
\end{figure}

>>>>

Technical advancements in linear optics have been made on many fronts that make it increasingly attractive for quantum computing applications. It is possible now to put single-photon sources and detectors together with linear-optical networks on a silica chip. The advantage of using such integrated photonics over bulk optics is that it is more stable against phase fluctuations, and miniaturized. This increases the scalability of optical implementations of quantum information protocols. Having all components on chip reduces coupling losses which would be crucial for fault-tolerant quantum computing. With the advantage of potentially piggybacking on existing communication infrastructure, and the relative ease of transporting quantum states of light, as compared to say trapped ions or superconducting qubits, it forms a powerful platform for quantum information processing.

In this review we will focus on single-photon encoding. Although other encodings, particularly those using continuous variable states of light exist, single-photon encodings seem to be the most promising. In the last decade, single photons have been produced mainly through spontaneous parametric down-conversion (SPDC), a nonlinear optical process. SPDC produces single photons in correlated pairs that has been the workhorse for providing entanglement in quantum states of light. Through much development in production schemes, and improvement in crystal quality, the number of high quality indistinguishable photons that can be concurrently produced have increased steadily over the years. Single-photon pairs are now run-of-the-mill business for quantum optical labs, and in the last five years, three photons are the landmark. The current record for single photons stand at ten. We have also seen the meteoric rise of quantum dots for this purpose. The latter has the advantage of on-demand single photon production, while SPDC is an inherently probabilistic process.

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=0.5\columnwidth]{reck}
\caption{Efficient decomposition of arbitrary linear optics networks into a sequence of beamsplitters and phase-shifters.} \label{fig:Reck}	
\end{figure}
